\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/introduction.tex
add references for spectre

Importantly, the trigger program and payload
program's indirect jump patterns diverge on the destination of their final jumps.
However, because the trigger program has trained the CPU's branch predictor, the
CPU speculates that the payload program will continue following the pattern of
the trigger program, causing it to speculatively execute a
\emph{target function} in the payload program. We emphasize that this target
function is in a region that is neither read nor executed by the payload
program, and after the CPU discovers the mis-speculation in the payload program,
it will discard the results from the target function and continue executing from
the correct destination. However, the payload program has a limited speculative
window where it can perform computation in the target function, and can
communicate results back to the ``real world'' payload program via a cache side
channel.

@@

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and evaluate their performance.
We find that the speculative window is limited by the reorder buffer
and physical register file sizes, which allows us to execute between 100 and 200 instructions
speculatively on modern Intel CPUs. While brief, we are able to perform
execution in short steps, communicating intermediate results back to the ``real
world'' part of the payload program. Using this technique,
we demonstrate implementing a universal Turing machine
(demonstrating arbitrary computation), a custom instruction set architecture
that fits within the constraints of speculative execution, and show
the ability to perform AES decryption
of a payload via AES encrypt/decrypt instructions.

>>>>

Importantly, the trigger program and payload program's indirect jump patterns
diverge on the destination of their final jumps. However, because the trigger
program has trained the CPU's branch predictor, the CPU speculates that the
payload program will continue following the pattern of the trigger program,
causing it to speculatively execute a \emph{target function} in the payload
program. This execution path is shown in Figure~\ref{fig:high-level}.

We emphasize that this target function is in a region that is neither
read nor executed by the payload program, and after the CPU discovers the
mis-speculation in the payload program, it will discard the results from the
target function and continue executing from the correct destination. However,
the payload program has a limited speculative window where it can perform
computation in the target function, and can communicate results back to the
``real world'' payload program via a cache side channel.

@@

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and evaluate their performance. We find that the speculative
window is limited by the reorder buffer and physical register file sizes, which
allows us to execute between 100 and 200 instructions speculatively on modern
Intel CPUs. While brief, we are able to perform execution in short steps,
communicating intermediate results back to the ``real world'' part of the
payload program. Using this technique, we demonstrate implementing a universal
Turing machine (demonstrating arbitrary computation), a custom instruction set
architecture that fits within the constraints of speculative execution, and show
the ability to perform AES decryption of a text block via AES encrypt/decrypt
instructions.
